% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


% load packages
\usepackage{geometry}
\usepackage{xcolor}
% \usepackage{eso-pic}
\usepackage{fancyhdr}
% \usepackage{sectsty} % conficts with titlesec
\usepackage{fontspec}
\usepackage[compact]{titlesec}
\usepackage{lipsum}
\usepackage{ragged2e}
\usepackage{enumitem}

%% Set page size using geometry
\geometry{letterpaper, left=12.5mm, top=12.5mm, bottom=12.5mm, right=12.5mm}

%% Let's define some colours using xcolor
\definecolor{light}{HTML}{CE03A9}
\definecolor{highlight}{HTML}{1F51FF} % Neon blue
\definecolor{dark}{HTML}{CE03A9} % Midnight blue 191970 #CE03A9 test pink

%%%%% Style the page number using fancyhdr, gets called in pagestyle.tex for BODY
\fancypagestyle{mystyle}{
  \fancyhf{}
  \renewcommand\headrulewidth{0pt}   %% define the thickness of a line under the header
  \fancyfoot[C]{Page \thepage} % Turn off for Cover Letter
  % \fancyfootoffset{1.5cm}
}
\setlength{\footskip}{15pt}   %% affects the page height

%%%%% style the chapter/section fonts -- see Advanced Interface in titlesec.pdf
% \chapterfont{\color{dark}\fontsize{20}{8}\selectfont}
% \sectionfont{\color{dark}\fontsize{20}{8}\selectfont}
% \subsectionfont{\color{dark}\fontsize{14}{8}\selectfont}
\titleformat{\subsection}{\sffamily\small\bfseries}{\thesection}{0em}{}[{\titlerule[0.8pt]}]

%%%%% left align title using `at sign' macros
\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft} %% left align with ragged right margin % \begin{center} %didnt work
  {\sffamily\huge\textbf{\@title}} \vspace{4pt} \newline
  {\Large {\@subtitle}} \vspace{0pt} % {\Large {\@author}} % \end{center}\egroup
\end{flushleft}\egroup
}
\makeatother

%% Use some custom fonts % I downloaded ROBOTO from google fonts
\setsansfont{Ubuntu}[
    Path=_extensions/nrennie/PrettyPDF/Ubuntu/,
    Scale=0.9,
    Extension = .ttf,
    UprightFont=*-Regular,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    ]

\setmainfont{Ubuntu}[
    Path=_extensions/nrennie/PrettyPDF/Ubuntu/,
    Scale=0.9,
    Extension = .ttf,
    UprightFont=*-Regular,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    ]
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}{}
\makeatother
\makeatletter
\@ifundefined{codebgcolor}{\definecolor{codebgcolor}{named}{light}}{}
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, colback={codebgcolor}, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Lauren Price, M.P.P., R.T.S.B.A.},
  colorlinks=true,
  linkcolor={highlight},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={highlight},
  pdfcreator={LaTeX via pandoc}}


\title{Lauren Price, M.P.P., R.T.S.B.A.}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Houston, TX \textbar{} 772-485-2635 \textbar{}
lauren.3.price@gmail.com \textbar{}
\href{https://www.linkedin.com/in/lauren-price-data/}{LinkedIn}
\textbar{} \href{https://github.com/pricele2}{GitHub} \textbar{}
\href{https://calendly.com/lauren-3-price/quick-chat}{Calendly}}
\author{}
\date{April 14, 2026}
\begin{document}
\maketitle


%% try \justifying to un-f the left align and ragged right margins
\justify

\setlength{\parindent}{0pt}
\setlist[itemize,1]{leftmargin=1em} % Sets leftmargin for all level 1 itemize lists

\pagestyle{mystyle}


\today

Director, Student Data Analytics \newline Denver Public Schools

Dear Hiring Committee:

I am pleased to apply for the position of Manager, Reporting and
Analytics (\#80734). This specific role would let me contribute my K-12
domain knowledge, technical skills, cutting-edge training, and
leadership to a K-12 city school district environment. I am deeply
passionate about the transformative power of public schools, and I am
actively seeking opportunities to relocate back to Colorado for family
reasons. In 2024, I saw DPS leaders present at the Council of Great City
Schools conference for Curriculum/Research Directors (Chicago, July
9-12). I was excited about the School Vitals dashboard, and I applauded
DPS for pulling in representatives from every department of the central
office for regular data MINE sessions with principals. I understand from
DPS board documents online that a more in-depth MINE process is underway
at targeted schools during the current school year.

The strongest candidate for this position will bring their unique
combination of four things: experience, skills, passions/values, and
personality. My professional experience and technical skills are laid
out in more detail in my attached full CV.

Briefly, after six years post-BA working in Colorado's nonprofit sector,
I went back to school full time to earn my Master's of Public Policy in
K-12 Education and Leadership. I excelled in the quant-heavy program,
regularly choosing doctoral-level courses to strengthen my methodology
chops. Since graduating, I have spent over a decade in K-12 public
education analytics, research, data governance, and regulatory
compliance. I proudly served the students, teachers, and families of my
community by doing thoughtful, clever work as an administrator in the
central office. With Houston ISD, I led cross-functional teams in
analytics initiatives and data product lifecycles, delivered accurate
and timely data to decision-makers, and implemented advanced data
science methodologies and complex district wide analytic products to
solve the District's business needs.

Since technology evolves quickly, I have also proactively stayed current
with new and emerging practices. In 2025, I participated in a targeted
professional training program to advance computational and analytic
capacity in K-12 education, funded by the Institute of Education
Sciences at the National Center for Educational Statistics. I was one of
20 selected from over 200 applicants to the Innovation Science for
Education Analytics (ISEA) training program, a sixteen-week curriculum
emphasizing state-of-the-art machine learning and AI strategies informed
by education domain knowledge, computational workflows, and immediate
applications for the K-12 environment. This deep training and its
culminating ``hackweek'' experience confirmed for me that ``human in the
loop'' data strategies have never been more important for K12 schools
and edtech providers.

As for the \emph{people} side of this technical role, I am an
experienced leader with six years of managing, coaching, and mentoring
technical analysts and stakeholder-facing program staff. As a
supervisor, I set high expectations and clear parameters, establish
collaborative practices and team norms, and then both oversee and coach
up where needed so our colleagues on other teams experience consistently
excellent results. I deliberately foster a high-performing, mutually
accountable team culture --- aiming to be the kind of leader that
educational theorist Dr.~Gloria Ladson-Billings might call a \emph{warm
demander}. But I also kindle a sense of together-ness, continuous
improvement through peer learning, and humor within my teams.

For example, during a high-stakes team project I proudly accepted a
meme-based compliment from a creative colleague highlighting my ability
to make machine-readable, reproducible, tidy data out of our
stakeholders' chaotic original files: \emph{Only Lauren can take this
messy pile of PPT and XLS files, and produce a Princess-Diaries-worthy
result.} We all laughed at the image, I taught them how to fork my
scripts and replicate the steps, and we met our deadlines even under the
time constraints.

Thank you for your consideration, and I hope to hear from your team
soon.

\vspace{12pt}

Regards,

Lauren Price




\end{document}
